Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
expe article

We first evaluate the curvature estimation on a full-resolution geometry
obtained by disabling the LoD criterion at the mesh generation step.
Figure~\ref{fig:full}-top and middle shows results of curvature tensor
estimation (mean, Gaussian, first and second principal curvatures, first and
second principal directions) on an OctaFlower at level $l_0$ (ground truth).
Figure~\ref{fig:full}-bottom shows mean curvature estimation in real-time on a
dynamic object. For all illustrations, we use directly normal vectors computed
by algorithm discussed in Section~\ref{sec:curv-tens-estim}.

@@

We can first note that the required time for an object to compute ground truth
curvature is usually as high as the time required to extract the geometry and
compute all the above levels. Using approximations is thus mandatory, since for
big objects such as the XYZ Dragon (Digital Domain $510^3$) with high radii, the
computation is seconds faster, the $l_0$ visualisation takes more than 4 seconds
to compute, whereas the approximated visualisation at $l_2$ takes only 300ms. We
can thus get an approximated visualisation of our object as soon as we run the
application, allowing for real time interactions with the object (changing the
visualised value, the curvature radius, etc ...). Once an interesting portion if
the object is reached, it only takes a few seconds to the application to display
ground truth curvature estimation.

It is also clear on those graphs that using a hierarchical decomposition reduces
the curvature computation time. For the XYZ Dragon with a radius of 20, it needs
almost 4 seconds to compute the $l_0$ level, whereas using the hierarchical
algorithm, it only needs 700ms. However, due to the precomputation, this
algorithm is biased and creates an error (presented in
Table~\ref{tab:full-res-stat}) that needs to be considered

%\subsection{Visualisation}
%
%For dynamic datasets, we consider a time varying implicit
%surface. Since it would have been to expensive to update the a mipmap texture
%of densities at each time step, we simply evaluate the implicit
%expression at each vertex of a cell to decide if such cell is included
%or not into $\Ball{R}{\vx}\cap \Shape$.
%\todo[inline]{blabla experiments}

>>>>

We first evaluate the curvature estimation on a full-resolution geometry
obtained by disabling the LoD criterion at the mesh generation step.
Figure~\ref{fig:full}-top and middle shows results of curvature tensor
estimation (mean, Gaussian, first and second principal curvatures, first and
second principal directions) on an OctaFlower at level $l_0$ (ground truth).
Figure~\ref{fig:full}-bottom shows mean curvature estimation in real-time on a
dynamic object. For this case, we simply evaluate the implicit expression at
each vertex of a cell to decide if such cell is included or not into
$\Ball{R}{\vx}\cap \Shape$ instead of updating the \emph{mipmap texture} of
densities at each time step. For all illustrations, we use directly normal
vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}.

@@

We can first note that the required time for an object to compute ground truth
curvature is usually as high as the time required to extract the geometry and
compute all the above levels. Using approximations is thus mandatory, since for
big objects such as the XYZ-Dragon ($510^3$) with big radii the approximate
computation is faster than the $l_0$ while results are enough close to the
$l_0$. For example, with $R=20$, the approximated visualization at $l_2$ takes
only $300$ms while the $l_0$ visualization takes more than $4$ seconds.

We can thus get an approximated visualisation of our object as soon as we run
the application, allowing for real time interactions with the object (changing
the visualized value, the curvature radius, \cdots). It is also clear on those
graphs that using a hierarchical decomposition reduces the curvature computation
time. For the XYZ-Dragon with $R=20$, it needs almost $4$ seconds to compute the
$l_0$ level, whereas using the hierarchical algorithm, it only needs $700$ms.
However, due to the precomputation, this algorithm is biased and creates an
error (presented in Table~\ref{tab:full-res-stat}) that needs to be considered.
